An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-08-24 latex_files/images/chapter4/mae2_hist_t2_romc_bo.tex
plots after changes

title={ROMC (Bayesian Optimisation) - \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0710656818158832);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.0516473550957937);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.194048417709784);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.2505503544856);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.348585934523831);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.648086654282988);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,0.583763447022691);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,0.929922090706508);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,0.79776958941701);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,0.987907371884556);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.05978215064711);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.2930717702704);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.55481463251829);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.01101046094927);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.35069632905971);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.34206596162857);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.80716185647295);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.71681269742808);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.65275918915001);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.45763197551135);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,2.24848041479702);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.8837125413398);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.80455589005721);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.47147764701123);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.35887832193294);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.990739211197902);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.834853199472739);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.568255755544842);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.531441844471339);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.415606131606362);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.366790615823915);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.350473827399395);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.220883466441019);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.136737383987297);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.185283200787522);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.154672366305157);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0558276893202577);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.179619522160829);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0788869523003634);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.625,0.0133500996200616);
\draw[draw=none,fill=color0] (axis cs:0.625,0) rectangle (axis cs:0.65,0.0134849491111732);
\draw[draw=none,fill=color0] (axis cs:0.65,0) rectangle (axis cs:0.675,0.00943946437782135);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.7,0.0140243470756202);
\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.725,0.00337123727779334);

@@

0.070389896781954 0
0.070389896781954 3

@@

\addlegendentry{$\mu = 0.070$}

@@

-0.131187651225067 1
0.236045424145365 1

@@

\addlegendentry{$\sigma = 0.167$}

>>>>

title={ROMC (Bayesian Optimisation) - Histogram of the parameter \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.00425643655908195);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0584436505421199);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.032329412084104);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.170488346927624);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.241312187040701);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.353203225767864);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.454783676389647);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,0.645870310110015);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,0.736855945766172);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,0.7054880882772);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,0.853720954547648);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.16488627133908);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.37944888929298);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.75863459008645);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.04186645728356);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,1.95487930439736);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.2931926651875);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.65546746491156);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.64247045528465);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.53538619434107);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.47437216167486);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,2.25894133814364);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,2.12306099510411);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.79209215192117);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.53877177811189);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.34176813031492);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.869256102075021);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.984211536278622);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.744495637346589);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.487332826886714);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.631223471040121);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.5510631368371);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.369415701030125);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.376101401475276);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.135239439335051);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.17253048109158);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.187926500765093);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.106413103399642);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0572991796412681);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0435129826888125);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.625,0.0491139237583741);
\draw[draw=none,fill=color0] (axis cs:0.625,0) rectangle (axis cs:0.65,0.011416843630065);
\draw[draw=none,fill=color0] (axis cs:0.65,0) rectangle (axis cs:0.675,0.0114168436300651);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.7,3.98076835078974e-05);
\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.725,0);

@@

0.0793529734576715 0
0.0793529734576715 3

@@

\addlegendentry{$\mu = 0.079$}

@@

-0.122023559466631 1
0.246600101073509 1

@@

\addlegendentry{$\sigma = 0.168$}
